Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/conclusion.tex

\subsection{Conclusion}
\label{sec:conclusion}

The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.

>>>>

The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
For modeling, it provides data on possible names for objects that constitutes a more robust testing ground.
In future work, we want to use ManyNames to fine-tune and examine  existing models in a multi-label setting towards a behavior that is more human-like.

For theoretical work, it provides name variation data with natural images and thus at the \textit{instance} level, as opposed to the category level that has been the focus up to now in theoretical work, due to the use of highly stylized drawings.
This affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as the prototypicality of the instance itself, or the effect of the visual context.

%However, it also comes with its own challenges, the main one being the issue of object identification, that we have found to interfere with the study of true naming variation. 
The use of naturalistic images in place of stylized drawings also comes with new challenges, which interfere with the study of naming variation: the factors inherently underlying variation cannot be easily separated from those introduced by issues such as object identification.
Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between true mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
Future work will need to address these challenges.

### 2019-05-21 papers/EMNLP2019/data-collection.tex

We take data from \vgenome \cite[\vg henceforth]{krishna2016visualgenome}, which
% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
contains a dense region-based labeling of $108k$~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs, 
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg is suitable for our purpose of collecting names for a relatively large amount of instances of common objects in
naturalistic images, as it has images of varying complexity, with close-ups as well as complex images with many objects.
As common in Computer Vision, objects are localized as 
%identified via
 bounding boxes (see red boxes in Figure~\ref{fig:cake}).% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

>>>>

We take data from \vg~\cite{krishna2016visualgenome}, which
% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
contains a dense region-based labeling of $108k$~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs, 
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
%As common in Computer Vision, O
Objects are localized as 
%identified via
 bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}
